Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2020-07-01 paper/ifo-conclusions.tex
intro and conclusion comments

In this paper we present an educational demonstration in which an \han{inexpensive} \jam{[see comments in introduction]}, table top Michelson interferometer serves as an analogue to a gravitational-wave detector. 
Vibrations produced by gravitational-wave signals are simulated with sound recordings played though a speaker fixed to the back of one of the interferometer mirrors. 
We consider quasi-monochromatic signals as an analogue to continuous wave signals as well as short segments of speech and music which are (more distant) analogues of unmodelled gravitational-wave bursts, e.g. from supernovae. 
% This serves to demonstrate signal processing techniques.

>>>>

In this paper we present an educational demonstration in which a table top Michelson interferometer serves as an analogue to a gravitational-wave detector. 
Vibrations produced by gravitational-wave signals are simulated with sound recordings played though a speaker fixed to the back of one of the interferometer mirrors. 
We consider quasi-monochromatic signals as an analogue to continuous wave signals as well as short segments of speech and music which are (more distant) analogues of unmodelled gravitational-wave bursts, e.g. from supernovae. 
% This serves to demonstrate signal processing techniques.

### 2020-07-01 paper/ifo-introduction.tex
intro and conclusion comments

% sound analogy
In this paper, we present an \han{inexpensive} \jam{["Inexpensive" is relative. The experiment is cheap compared to LIGO, but out of budget for a high-school. Suggestions: "modest", "simple", or just cut the adjective.]} table-top experiment, where a standard Michelson interferometer plays the role of a `toy' gravitational-wave detector, which detects acoustic vibrations (such as music) instead of gravitational waves. 
As an undergraduate lab experiment this demonstration can be used to teach topics ranging from gravitational-wave detection and analysis to electronics, signal processing, and speech enhancement. 
It gives students in courses such as physics and electrical engineering the freedom to explore the response of an accessible yet nontrivial opto-mechanical system using a hierarchy of data analysis techniques of increasing complexity, including those used in the search for continuous waves in LIGO and Virgo data~\cite{ScoX1O2Viterbi:2019,ScoX1ViterbiO1:2017,SuvorovaEtAl:2017,SuvorovaEtAl:2017}.
The demonstration can also be adapted for use as an outreach tool to explain gravitational-wave science to a general audience.

>>>>

% sound analogy
In this paper, we present a table-top experiment, where a standard Michelson interferometer plays the role of a `toy' gravitational-wave detector, which detects acoustic vibrations (such as music) instead of gravitational waves. 
As an undergraduate lab experiment this demonstration can be used to teach topics ranging from gravitational-wave detection and analysis to electronics, signal processing, and speech enhancement. 
It gives students in courses such as physics and electrical engineering the freedom to explore the response of an accessible yet nontrivial opto-mechanical system using a hierarchy of data analysis techniques of increasing complexity, including those used in the search for continuous waves in LIGO and Virgo data~\cite{ScoX1O2Viterbi:2019,ScoX1ViterbiO1:2017,SuvorovaEtAl:2017,SuvorovaEtAl:2017}.
The demonstration can also be adapted for use as an outreach tool to explain gravitational-wave science to a general audience.

### 2020-07-01 paper/ifo-tableTopGWs.tex
intro and conclusion comments

Gravitational-wave detectors are large, complex interferometers.
The LIGO and Virgo detectors have $4\,{\rm km}$ and $3\,{\rm km}$ arms respectively.
They are sensitive to minuscule changes in distance, for example the first detection of a binary black hole merger had a peak gravitational-wave strain of $10^{-21}$ ~\cite{GW150914}.
However, their design is based fundamentally on the Michelson interferometer. 
Detection and analysis concepts can be demonstrated with table-top optical equipment.

@@

\han{to do: add some text referring to other demo designs and references:~\cite{TTExhibit:2020,TTExhibit:online,ThorLabsIFO,LIGOIFOGlue,LIGOIFOMagnets,FoxEtAl:1999}. }
% Note that we do not include the common compensating plate that equalises the amount of time spent in glass for each beam. We did not find it necessary to include it to be able to demonstrate the results desired.

\jam{[I don't know what these other designs are (haven't seen the references), is this something that the Adelaide people would have used in their design?]}

>>>>

Gravitational-wave detectors are large, complex interferometers.
The LIGO and Virgo detectors have $4\,{\rm km}$ and $3\,{\rm km}$ arms respectively.
They are sensitive to minuscule changes in distance, for example the first detection of a binary black hole merger had a peak gravitational-wave strain of $10^{-21}$ ~\cite{GW150914}.
However, their design is based fundamentally on the Michelson interferometer. 
Detection and analysis concepts can be demonstrated with table-top optical equipment. 
See Refs.~\cite{TTExhibit:2020,TTExhibit:online,ThorLabsIFO,LIGOIFOGlue,LIGOIFOMagnets,FoxEtAl:1999} for a selection of table-top Michelson interferometer designs used for science communication.

@@
